Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-29 manuscript/manuscript.tex
Edits to the sinusoidal case
Added some more justification of why we're doing this (to show that we
can). Added missing definition of A and its value. delta=0.1 is good for
all but the most extreme case, emphasize that. Point out that even if
delta=0.1, the error is below 1% for b=10.

We will consider spherical shells with a sinusoidal density defined as follows:

\begin{equation}
    \rho(r') = A \sin \left( 2 \pi b \frac{r' - R}{T} \right) + A,
    \label{eq:density-sine}
\end{equation}

\noindent where $A$ is a constant, $T$ is the thickness of the shell, $R$ is the mean
Earth radius and $b$ is a dimensionless constant that regulates how many periods of the
trigonometric function are included inside the inner and outer radii.
For this analysis we will use values of $b$ equal to 1, 2, 5 and 10
(Fig.~\ref{fig:sine-densities}).
We shift the sine function in order to prevent near zero values of the potential and the
$g_z$.

We compute the relative difference between the numerical and analytical results for the
gravitational potential ($V$) and the $g_z$ of the spherical shells detailed in
Table~\ref{tab:shell-models} on each grid detailed in Table~\ref{tab:grids}.
Each shell is assigned with different sinusoidal density functions by changing the
values of $b$ in Eq.~\ref{eq:density-sine} (Fig.~\ref{fig:sine-densities}).
The analytical solution for the potential $V$ can be found on Appendix~\ref{sec:shell}.
We fixed the distance-size ratio $D$ to the ones obtained for the linear density case
and explored values of $\delta$ ranging from $10^{-4}$ to $1$.

\begin{figure}
\centering
\iftwocol{
\includegraphics[width=\linewidth]{figures/sine-densities.pdf}
}{
\includegraphics[width=0.5\linewidth]{figures/sine-densities.pdf}
}
\caption{
    Sinusoidal density functions assigned to each spherical shell in the $\delta$ ratio
    determination.
    Each density function corresponds to a different value of $b$ on
    Eq.~\ref{eq:density-sine}.
}
\label{fig:sine-densities}
\end{figure}

@@

Fig.~\ref{fig:sine-densities} shows the sinusoidal density functions assigned to every
spherical shell and Fig.~\ref{fig:delta-sine} shows the resulting relative differences
between the analytical and the numerical solutions.
In order to improve the visualization of the results, each curve corresponds to the
maximum difference between all shell models for the same value of $b$.
For this kind of sinusoidal density, a value of $\delta=0.01$ is needed in order to
achieve the 0.1\% accuracy threshold for both the potential and the $g_{z}$, every
shell model, computation grid and value of $b$.
Even in case of a continuous density function with several local maximums and minimums
and inflection points, the GLQ along with the two discretization algorithms reproduce
the gravitational fields with an acceptable degree of accuracy.

>>>>

We will consider spherical shells with a sinusoidal density function defined as follows:

\begin{equation}
    \rho(r') = A \sin \left( 2 \pi b \frac{r' - R}{R_2 - R_1} \right) + A,
    \label{eq:density-sine}
\end{equation}

\noindent in which $A$ is a constant that controls the amplitude and vertical shift of
the sine function, $R$ is the mean Earth radius, and $b$ is a dimensionless constant
that regulates how many periods of the trigonometric function are included inside the
inner and outer radii.
The analytical solutions for $V$ and $g_z$ of a spherical shell with a sinusoidal
density function can be found on Appendix~\ref{sec:shell}.

We compute the relative difference between the numerical and analytical results for $V$
and $g_z$ for all combinations of spherical shell models (Table~\ref{tab:shell-models})
and computation grids (Table~\ref{tab:grids}).
We fixed the distance-size ratio $D$ to the ones obtained for the linear density case
and explored values of $\delta$ ranging from $10^{-4}$ to $1$.
The calculations are repeated for values of $b$ equal to 1, 2, 5 and 10
(Fig.~\ref{fig:sine-densities}).
For all computations, the value of $A$ is fixed at 1650 kg/m$^3$.

\begin{figure}
\centering
\iftwocol{
\includegraphics[width=\linewidth]{figures/sine-densities.pdf}
}{
\includegraphics[width=0.5\linewidth]{figures/sine-densities.pdf}
}
\caption{
    Sinusoidal density functions assigned to the spherical shells in the $\delta$ ratio
    determination.
    Each density function corresponds to a different value of $b$ on
    Eq.~\ref{eq:density-sine}.
}
\label{fig:sine-densities}
\end{figure}

@@

Fig.~\ref{fig:delta-sine} shows the relative absolute differences between the analytical
and the numerical solutions for sinusoidal density case.
Once again, each curve corresponds to the maximum difference between all shell models.
For all values of $b$ except for $b=10$,
the differences fall below the 0.1\% threshold for $\delta = 0.1$.
In the case of $b=10$, a lower value of $\delta = 0.01$ is required to achieve 0.1\%
difference.
We note that, even for the case of $b=10$, the differences for $\delta = 0.1$ are below
1\%.
